### 2020-04-27 Temp_tables/Temp_tables_revision/00_Archive/03_foreign.tex
back up before new paper

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Mar 08, 2020 - 11:09:36
\begin{table}[!htbp] \centering 
  \caption{Baseline results revision: Foreign-SOE} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{The Dependent variable:} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.395$^{*}$ & $-$0.574$^{**}$ & $-$0.329 & $-$0.294 & $-$0.435 & $-$0.342 \\ 
  & (0.239) & (0.253) & (0.246) & (0.275) & (0.285) & (0.277) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.733 &  &  & 0.464 &  &  \\ 
  & (0.880) &  &  & (1.155) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{i}  & $-$0.419 &  &  & $-$0.706 &  &  \\ 
  & (0.444) &  &  & (0.609) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & 0.513 &  &  & 0.073 &  &  \\ 
  & (1.501) &  &  & (1.700) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  & 1.303$^{**}$ &  &  & 1.278$^{*}$ &  &  \\ 
  & (0.594) &  &  & (0.697) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.859 &  &  & 0.082 &  \\ 
  &  & (0.881) &  &  & (1.047) &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}  &  & $-$0.341 &  &  & $-$0.661 &  \\ 
  &  & (0.369) &  &  & (0.472) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & 1.471 &  &  & 0.627 &  \\ 
  &  & (1.271) &  &  & (1.436) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  & 1.099$^{**}$ &  &  & 1.176$^{**}$ &  \\ 
  &  & (0.498) &  &  & (0.579) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & $-$0.045 &  &  & 0.937 \\ 
  &  &  & (0.858) &  &  & (1.094) \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}  &  &  & $-$0.168 &  &  & $-$0.727 \\ 
  &  &  & (0.473) &  &  & (0.632) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & 0.031 &  &  & 0.161 \\ 
  &  &  & (1.665) &  &  & (1.761) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  & 0.994 &  &  & 1.384$^{**}$ \\ 
  &  &  & (0.608) &  &  & (0.702) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{6}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Mar 08, 2020 - 11:14:33
\begin{table}[!htbp] \centering 
  \caption{Baseline results revision: Foreign} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{The Dependent variable:} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.083 & $-$0.170 & $-$0.042 & $-$0.021 & $-$0.049 & 0.011 \\ 
  & (0.185) & (0.177) & (0.166) & (0.214) & (0.210) & (0.195) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.483 &  &  & 0.856 &  &  \\ 
  & (0.808) &  &  & (1.031) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & $-$0.595 &  &  & $-$0.874 &  &  \\ 
  & (1.398) &  &  & (1.539) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.535 &  &  & 0.650 &  \\ 
  &  & (0.781) &  &  & (0.923) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & 0.233 &  &  & $-$0.555 &  \\ 
  &  & (1.148) &  &  & (1.296) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & 0.079 &  &  & 1.437 \\ 
  &  &  & (0.750) &  &  & (0.929) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & $-$0.983 &  &  & $-$1.061 \\ 
  &  &  & (1.523) &  &  & (1.572) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{6}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/01_Herfindhal/06_conc_ind_soe.tex
back up before new paper

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Mar 08, 2020 - 11:14:33
\begin{table}[!htbp] \centering 
  \caption{Baseline results revision: Foreign} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{The Dependent variable:} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.083 & $-$0.170 & $-$0.042 & $-$0.021 & $-$0.049 & 0.011 \\ 
  & (0.185) & (0.177) & (0.166) & (0.214) & (0.210) & (0.195) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.483 &  &  & 0.856 &  &  \\ 
  & (0.808) &  &  & (1.031) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & $-$0.595 &  &  & $-$0.874 &  &  \\ 
  & (1.398) &  &  & (1.539) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.535 &  &  & 0.650 &  \\ 
  &  & (0.781) &  &  & (0.923) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & 0.233 &  &  & $-$0.555 &  \\ 
  &  & (1.148) &  &  & (1.296) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & 0.079 &  &  & 1.437 \\ 
  &  &  & (0.750) &  &  & (0.929) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & $-$0.983 &  &  & $-$1.061 \\ 
  &  &  & (1.523) &  &  & (1.572) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{6}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Mar 08, 2020 - 12:20:15
\begin{table}[!htbp] \centering 
  \caption{Baseline results revision: concentration} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{The Dependent variable:} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.032 & $-$0.142 & $-$0.097 & 0.086 & 0.037 & 0.060 \\ 
  & (0.639) & (0.643) & (0.635) & (0.698) & (0.688) & (0.679) \\ 
   TCZ_c \times \text{Period} \times \text{Herfindahl}_{i} & 0.029 & 0.013 & 0.013 & 0.451 & 0.491 & 0.528 \\ 
  & (0.819) & (0.810) & (0.818) & (0.946) & (0.943) & (0.914) \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{i}  & $-$0.199 &  &  & $-$0.944$^{*}$ &  &  \\ 
  & (0.431) &  &  & (0.533) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}  &  & $-$0.103 &  &  & $-$0.774$^{*}$ &  \\ 
  &  & (0.325) &  &  & (0.408) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}  &  &  & $-$0.137 &  &  & $-$1.148$^{**}$ \\ 
  &  &  & (0.441) &  &  & (0.518) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{Herfindahl}_{i} & $-$0.404 & $-$0.240 & $-$0.345 & $-$0.597 & $-$0.582 & $-$0.687 \\ 
  & (0.932) & (0.937) & (0.931) & (1.034) & (1.019) & (1.001) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  & 1.216$^{**}$ &  &  & 1.478$^{**}$ &  &  \\ 
  & (0.586) &  &  & (0.649) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  & 0.787$^{*}$ &  &  & 1.175$^{**}$ &  \\ 
  &  & (0.459) &  &  & (0.541) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  & 1.048$^{*}$ &  &  & 1.702$^{***}$ \\ 
  &  &  & (0.572) &  &  & (0.612) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{6}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/011_output_industry_cum.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 10:34:53
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.226 & $-$0.353 & $-$1.304$^{***}$ & $-$0.582 & $-$0.237 & $-$0.010 & $-$0.018 & 0.331 & 0.316 \\ 
  & (0.562) & (0.471) & (0.422) & (0.607) & (0.474) & (0.266) & (0.343) & (0.319) & (0.407) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 929 & 1,898 & 2,922 & 2,263 & 3,718 & 3,705 & 5,574 & 3,458 & 3,874 \\ 
R$^{2}$ & 0.966 & 0.893 & 0.900 & 0.895 & 0.877 & 0.905 & 0.881 & 0.896 & 0.889 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:04:13
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.226 & $-$0.682 & $-$0.789$^{**}$ & $-$0.657$^{**}$ & $-$0.432$^{**}$ & $-$0.297$^{*}$ & $-$0.190 & $-$0.199 & $-$0.148 \\ 
  & (0.562) & (0.461) & (0.326) & (0.270) & (0.215) & (0.162) & (0.141) & (0.132) & (0.123) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 929 & 2,827 & 5,749 & 8,012 & 11,730 & 15,435 & 21,009 & 24,467 & 28,341 \\ 
R$^{2}$ & 0.966 & 0.893 & 0.877 & 0.862 & 0.849 & 0.857 & 0.853 & 0.850 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/020_capital_industry_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:04:13
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.226 & $-$0.682 & $-$0.789$^{**}$ & $-$0.657$^{**}$ & $-$0.432$^{**}$ & $-$0.297$^{*}$ & $-$0.190 & $-$0.199 & $-$0.148 \\ 
  & (0.562) & (0.461) & (0.326) & (0.270) & (0.215) & (0.162) & (0.141) & (0.132) & (0.123) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 929 & 2,827 & 5,749 & 8,012 & 11,730 & 15,435 & 21,009 & 24,467 & 28,341 \\ 
R$^{2}$ & 0.966 & 0.893 & 0.877 & 0.862 & 0.849 & 0.857 & 0.853 & 0.850 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:17:52
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.409 & $-$0.894$^{**}$ & 1.151 & $-$0.768$^{*}$ & $-$0.134 & $-$0.560 & 0.121 & $-$0.076 & 0.910$^{***}$ \\ 
  & (0.569) & (0.349) & (0.820) & (0.437) & (0.388) & (0.436) & (0.274) & (0.611) & (0.337) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,503 & 2,377 & 2,195 & 3,028 & 4,428 & 4,126 & 3,630 & 2,643 & 3,768 \\ 
R$^{2}$ & 0.925 & 0.901 & 0.903 & 0.884 & 0.896 & 0.885 & 0.920 & 0.908 & 0.888 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/021_capital_industry_cum.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:04:13
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.226 & $-$0.682 & $-$0.789$^{**}$ & $-$0.657$^{**}$ & $-$0.432$^{**}$ & $-$0.297$^{*}$ & $-$0.190 & $-$0.199 & $-$0.148 \\ 
  & (0.562) & (0.461) & (0.326) & (0.270) & (0.215) & (0.162) & (0.141) & (0.132) & (0.123) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 929 & 2,827 & 5,749 & 8,012 & 11,730 & 15,435 & 21,009 & 24,467 & 28,341 \\ 
R$^{2}$ & 0.966 & 0.893 & 0.877 & 0.862 & 0.849 & 0.857 & 0.853 & 0.850 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:19:11
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.409 & $-$0.803$^{***}$ & $-$0.563 & $-$0.544$^{**}$ & $-$0.332$^{*}$ & $-$0.317$^{**}$ & $-$0.272$^{**}$ & $-$0.248$^{*}$ & $-$0.136 \\ 
  & (0.569) & (0.263) & (0.350) & (0.245) & (0.173) & (0.150) & (0.131) & (0.130) & (0.127) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,503 & 3,880 & 6,075 & 9,103 & 13,531 & 17,657 & 21,287 & 23,930 & 27,698 \\ 
R$^{2}$ & 0.925 & 0.889 & 0.871 & 0.855 & 0.858 & 0.852 & 0.856 & 0.855 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}
